### 2023-02-21 glossaries/acronyms.tex
Up
Minor changes
mostly units

\newacronym[symbol={\mathrm{CHL}}, sort=ChlA]
    {chl}{Chl\babelhyphen{nobreak}\emph{a}}{Chlorophyll\babelhyphen{nobreak}\emph{a}}
\newacronym[symbol={\mathrm{SST}}]
    {sst}{SST}{Sea Surface Temperature}

\newacronym[symbol={\mathrm{HI}}]
    {hi}{HI}{Heterogeneity Index}

\newacronym{avhrr}{AVHRR}{Advanced Very"-High"-Resolution Radiometer}
\newacronym{viirs}{VIIRS}{Visible Infrared Imaging Radiometer Suite}
\newacronym{modis}{MODIS}{Moderate Resolution Imaging Spectroradiometer}
\newacronym[sort=AATSR]{atsr}{(A)ATSR}{(Advanced) Along Track"-Scanning Radiometer}
\newacronym{seawifs}{SeaWiFS}{Sea-viewing Wild Field"-of"-view Sensor}
\newacronym{meris}{MERIS}{Medium Resolution Imaging Spectrometer}
\newacronym{olci}{OLCI}{Ocean and Land Colour Instrument}

@@

\newacronym
[description={Groupe fonctionnel phytoplanctonique}]
{pft}{PFT}{Phytoplanktonic Function Type}

>>>>

\newacronym{avhrr}{AVHRR}{Advanced Very"-High"-Resolution Radiometer}
\newacronym{viirs}{VIIRS}{Visible Infrared Imaging Radiometer Suite}
\newacronym{modis}{MODIS}{Moderate Resolution Imaging Spectroradiometer}
\newacronym[sort=AATSR]{atsr}{(A)ATSR}{(Advanced) Along Track"-Scanning Radiometer}
\newacronym{slstr}{SLSTR}{Sea and Land Surface Temperature Radiometer}
\newacronym{seawifs}{SeaWiFS}{Sea-viewing Wild Field"-of"-view Sensor}
\newacronym{meris}{MERIS}{Medium Resolution Imaging Spectrometer}
\newacronym{olci}{OLCI}{Ocean and Land Colour Instrument}
\newacronym[description={Joint Polar Satellite System, JPSS-1 = NOAA-20}]
{jpss}{JPSS}{Joint Polar Satellite System}

@@

\newacronym%
[description={Groupe fonctionnel phytoplanctonique}]
{pft}{PFT}{Phytoplanktonic Function Type}
